Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Added graphs.

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

@@

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
weakened forms of degree and path based filterings are still effective in pruning the initial search
space and in providing additional constraints respectively. We then show that combining these
techniques leads to a practical algorithm which can scale to work with the families of graphs
commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound. This is a
significant improvement over state of the art maximum common subgraph solvers, which cannot even fit
many of these instances in RAM.

\subsection{Definitions and Notations}

@@

\todo{is this example graph still needed?? yes, Patrick likes pictures}

>>>>

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds,shapes.misc}
%cross
\tikzset{cross/.style={cross out, draw=uofgcobalt, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1.5mm}}

@@

In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
weakened forms of degree and path based filterings are still effective in pruning the initial search
space and in providing additional constraints respectively. We then show that combining these
techniques leads to a practical algorithm which can scale to work with the families of graphs
commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound. This is a
significant improvement over state of the art maximum common subgraph solvers, which cannot even fit
many of these instances in RAM.
\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
            \node[fill=uofgcobalt] (a) {};
            \node (a1) [below left of = a] {};
            \node (b1) [below right of = a] {};
            \node (aa) [below right of = a1] {};

            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ac2) [fill=gray!70,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bc2) [fill=gray!70,above right of = bb2,node distance=13mm,xshift=2mm] {};

            \node (aaa) [below of =aa, node distance=20mm] {};

            \path[dotted] (a) edge (a1) edge (b1);
            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
                (a1) edge (b1)
                (aaa) edge (a2) edge (b2)
                (a2) edge (aa2) edge (ab2)
                (b2) edge (ba2) edge (bb2);
            \path[color=gray!70] (ac2) edge (ab2) edge (aa2)
                (bc2) edge (bb2) edge (ba2);

            \node [cross] {};
        \end{tikzpicture}
        \caption{Example of  ``as much of the pattern'' as possible.}
        \label{fig:subgraphexample}
    \end{center}
\end{figure}
\subsection{Definitions and Notations}

@@

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (p) {};
            \node[fill=black] (b) [above of = p,node distance=10mm] {};
            \node[fill=black] (a) [left of = b] {};
            \node[fill=black] (c) [right of = b] {};
            \node[fill=black] (d) [above of = b,node distance=10mm] {};

            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
            \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
            \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
            \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};

            \node[draw=none, below of = p, node distance=6mm] {$P$};

            \path (p) edge (a) edge (b) edge (c)
                (a) edge (d)
                (b) edge (c) edge (d)
                (c) edge (d);
        \end{tikzpicture}

        \vspace{5mm}

        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (a1) {};
            \node[fill=black] (b1) [right of = a1] {};
            \node[fill=black] (c1) [right of = b1] {};
            \node[fill=black] (a2) [below of = a1] {};
            \node[fill=black] (b2) [right of = a2] {};
            \node[fill=black] (c2) [right of = b2] {};
            \node[fill=black] (a3) [below of = a2] {};
            \node[fill=black] (b3) [right of = a3] {};
            \node[fill=black] (c3) [right of = b3] {};

            \node[draw=none, below of = b3, node distance=6mm] {$T_{1}$};

            \path[color=gray!70] (a1) edge (b1) edge (a2)
                (b1) edge (c1)
                (c1) edge (c2)
                (a2) edge (b2) edge (a3)
                (c2) edge (c3)
                (a3) edge (b3)
                (b3) edge (c3);
            \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
                (a2) edge (b3)
                (b2) edge (c2) edge (b3)
                (c2) edge (b3);
        \end{tikzpicture}
        \hspace{1cm}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
            \node[fill=black] (p) {};
            \node[draw=none] (b) [above of = p,node distance=10mm] {};
            \node[fill=black] (a) [left of = b] {};
            \node[fill=black] (c) [right of = b] {};
            \node[fill=black] (d) [above of = b,node distance=10mm] {};

            \node[draw=none, below of = p, node distance=6mm] {$T_{2}$};

            \path (p) edge (a) edge (c)
                (a) edge (d)
                (c) edge (d);
        \end{tikzpicture}
        \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
        \label{fig:klessexample}
    \end{center}
\end{figure}
